---
title: "pull budget data"
author: "John D. Smith"
date: "3/27/2017"
output: html_document

---
```{r}
library(stringr)
library(tidyverse)
library(lubridate)
library(tidyr)
library(jsonlite)
library(hrbrthemes)
source("~/Rfunctions/setup_my_google.R")
source("~/Rfunctions/make_dd.R")
# source("https://raw.githubusercontent.com/smithjd/Rfunctions/master/setup_my_google.R")
# source("https://raw.githubusercontent.com/smithjd/Rfunctions/master/make_dd.R")

```
 "fund_center_code": "PSCO000001",
        "fund_code": "GENERAL",
        "functional_area_code": "LACOAS",
        "object_code": "EMS",
        "fund_center_name": "Commissioner of Public Safety",
        "fund_name": "General Fund",
        "functional_area_name": "Commissioner's Office",
        "accounting_object_name": "External Materials and Services",
        "service_area_code": "LA",
        "program_code": "LACO",
        "sub_program_code": "LACOAS",
        "fund_center": "PSCO000001",
        "division_code": "PSCO",
        "bureau_code": "PS",
        "bureau_name": "Commissioner of Public Safety",
        "fiscal_year": "2015-16",
        "amount": 12251


```{r}
cost_url <- file("http://hacko-integration-658279555.us-west-2.elb.amazonaws.com/budget/code/")
cost_raw <- read_file(cost_url)
cost_df <- fromJSON(cost_raw)
```
get history data
```{r}
# ps_15 <- fromJSON("http://hacko-integration-658279555.us-west-2.elb.amazonaws.com/budget/history/?fiscal_year=2015-16&bureau_code=PS")
ps_15 <- fromJSON("http://hacko-integration-658279555.us-west-2.elb.amazonaws.com/budget/history/?bureau_code=PS")

```
Look at all fund transfers for all years FNDXFER
```{r}
fund_transfer <- fromJSON("http://hacko-integration-658279555.us-west-2.elb.amazonaws.com/budget/history/?object_code=FNDXFER") %>% filter(amount != 0)

ggplot(fund_transfer, aes(fiscal_year, amount)) +
  geom_bar(stat = "identity") +
  theme_ipsum()

ggplot(fund_transfer, aes(bureau_name, amount)) +
  geom_bar(stat = "identity", aes(fill = fiscal_year)) +
   coord_flip() +
   theme_ipsum()
```

Look at all fund transfers for all years PERSONAL
```{r}
peronsal <- fromJSON("http://hacko-integration-658279555.us-west-2.elb.amazonaws.com/budget/history/?object_code=EMS") %>% filter(amount != 0)

ggplot(personal, aes(fiscal_year, amount)) +
  geom_bar(stat = "identity") +
  theme_ipsum()

ggplot(personal, aes(bureau_name, amount)) +
  geom_bar(stat = "identity", aes(fill = fiscal_year)) +
   coord_flip() +
   theme_ipsum()
```
Browse the whole dataset
```{r}
> library(readr)
> dataset <- read_csv("./data/HackOregon_hx_budget_data_ASV2_transformed.csv")
```

